---
title: "Final Project"
description: "Ballard Kauffman and Anna Leidner"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
library(tidyverse)     # for data cleaning and plotting
library(gardenR)       # for Lisa's garden data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(patchwork)     # for nicely combining ggplot2 graphs  
library(gt)            # for creating nice tables
library(rvest)         # for scraping data
library(robotstxt)     # for checking if you can scrape data
library(janitor)       # for cleaning names
# library(baseballr)
# library(sportyR)
# library(pitchRx)
# library(Lahman)


baseballdata <- read.csv("https://raw.githubusercontent.com/aleidner6/FinalProject/main/baseballfinalproject.csv")

#baseball data of hitters from 2015-2022 season. Some important stats to note are woba, xwoba, EV, and LA. If you want to look at other/more stats or for specific players go for it!
```

Introduction and Background: An introduction that motivates & outlines a clear, specific set of research questions. Also, provide some background on your topic.

Data collection: Specification of your data sources and collection process.

Analysis: This is the bulk of the report which either has a presentation of the group’s key findings and take-aways or gives the detail of how someone would interact and what people should take away from the shiny app. If you choose to do a shiny app, be sure to include a link to the shinyapps.io site.
